\chapter{\textit{Across the Moor}}
\lettrine{S}{he} slept a long time, and when she awakened Mrs. Medlock had bought a lunchbasket at one of the stations and they had some chicken and cold beef and bread and butter and some hot tea. The rain seemed to be streaming down more heavily than ever and everybody in the station wore wet and glistening\footnote{\textbf{glisten} v. to shine with light reflected off a wet surface} waterproofs\footnote{\textbf{waterproof} n. \textit{(Brit)} raincoat}. The guard lighted the lamps in the carriage, and Mrs. Medlock cheered up very much over her tea and chicken and beef. She ate a great deal and afterward fell asleep herself, and Mary sat and stared at her and watched her fine bonnet slip on one side until she herself fell asleep once more in the corner of the carriage, lulled\footnote{\textbf{lull} v. to cause (someone) to fall asleep or become sleepy} by the splashing of the rain against the windows. It was quite dark when she awakened again. The train had stopped at a station and Mrs. Medlock was shaking her.

``You have had a sleep!'' she said. ``It's time to open your eyes! We're at Thwaite Station and we've got a long drive before us.''

The station was a small one and nobody but themselves seemed to be getting out of the train. The station-master spoke to Mrs. Medlock in a rough, good-natured way, pronouncing his words in a queer broad fashion which Mary found out afterward was Yorkshire.

``I see tha's got back,'' he said. ``An' tha's browt th' young 'un with thee.''

``Aye, that' her,'' answered Mrs. Medlock, speaking with a Yorkshire accent herself and jerking her head over her shoulder toward Mary. ``How's thy Missus?''

``Well enow. Th' carriage is waitin' outside for thee.''

A brougham\footnote{\textbf{brougham} n. A brougham was a light, four-wheeled horse-drawn carriage built in the 19th century} stood on the road before the little outside platform. Mary saw that it was a smart carriage and that it was a smart footman\footnote{\textbf{footman} n. a male servant who lets visitors into a house and serves food at the dinner table} who helped her in. His long waterproof coat and the waterproof covering of his hat were shining and dripping\footnote{\textbf{drip} v. to fall in drops} with rain as everything was, the burly\footnote{\textbf{burly} adj. strong and heavy} station-master included.

When he shut the door, mounted the box with the coachman, and they drove off, the little girl found herself seated in a comfortably cushioned\footnote{\textbf{cushion} v. (\textbf{adj.} cushioned) to make (something, such as a fall or collision) less severe or painful} corner, but she was not inclined\footnote{\textbf{inclined} adj. wanting to do something or likely to do something} to go to sleep again. She sat and looked out of the window, curious to see something of the road over which she was being driven to the queer place Mrs. Medlock had spoken of. She was not at all a timid\footnote{\textbf{timid} adj. feeling or showing a lack of courage or confidence} child and she was not exactly frightened, but she felt that there was no knowing what might happen in a house with a hundread rooms nearly all shut up--a house standing on the edge of a moor.

``What is a moor?'' she said suddenly to Mrs. Medlock.

``Look out of the window in about ten minutes and you'll see,'' the woman answered. ``We've got to drive five miles across Missel Moor before we get to the Manor. You won't see much because it's a dark night, but you can see something.''

Mary asked no more questions but waited in the darkness of her corner, keeping her eyes on the window. The carriage lamps cast rays of light a little distance ahead of them and she caught glimpses\footnote{\textbf{glimpse} n. a brief or quick view or look} of the things they passed. After they had left the station they had driven through a tiny village and she had seen whitewashed cottages and the lights of a public house. Then they had passed a church and a vicarage\footnote{\textbf{vicarage} n. a vicar's home} and a little shop-window or so in a cottage with toys and sweets and odd things set out for sale. Then they were on the highroad and she saw hedges\footnote{\textbf{hedge} n. a row of shrubs or small trees that are planted close to each other in order to form a boundary} and trees. After that there seemed nothing different for a long time--or at least it seemed a long time to her.

At last the horses began to go more slowly, as if they were climbing up-hill, and presently there seemed to be no more hedges and no more trees. She could see nothing, in fact, but a dense\footnote{\textbf{dense} adj. difficult to see through} darkness on either side. She leaned forward and pressed her face against the window just as the carriage gave a big jolt\footnote{\textbf{jolt} n. a sudden, rough movement}.

``Eh! We're on the moor now sure enough,'' said Mrs. Medlock.

The carriage lamps shed\footnote{\textbf{shed} v. (\textbf{pt./pp.} shed) to get rid of (something); radiate} a yellow light on a rough-looking road which seemed to be cut through bushes and low-growing things which ended in the great expanse\footnote{\textbf{expanse} n. a large and usually flat open space or area} of dark apparently spread out before and around them. A wind was rising and making a singular, wild, low, rushing sound.

``It's--it's not the sea, is it?'' said Mary, looking round at her companion.
