\lettrine{A}{nd} after all the weather was ideal. They could not have had a more perfect day for a garden-party if they had ordered it. Windless, warm, the sky without a cloud. Only the blue was veiled\footnote{\textbf{veil} v. to cover sth with sth that hides it partly or completely} with a haze\footnote{\textbf{haze} n. air containing sth that makes it difficult to see through it} of light gold, as it is sometimes in early summer. The gardener had been up since dawn, mowing\footnote{\textbf{mow} v. to cut grass etc. using a machine or tool with a special blade or blades} the lawns\footnote{\textbf{lawn} n. an area of ground in short grass in a garden/yard or park, or used for playing a game} and sweeping them, until the grass and the dark flat rosettes\footnote{\textbf{rosette} n. a thing that has the shape of a rose} where the daisy\footnote{\textbf{daisy} n. a small wild flower with white petals around a yellow centre} plants had been seemed to shine. As for the roses, you could not help feeling they understood that roses are the only flowers that impress people at garden-parties; the only flowers that everybody is certain of knowing. Hundreds, yes, literally hundreds, had come out in a single night; the green bushes bowed\footnote{\textbf{bow} v. to bend or make sth bend} down as though they had been visited by archangels.

Breakfast was not yet over before men came to put up the marquee\footnote{\textbf{marquee} n. a large tent used at social events}.

``Where do you want the marquee put, mother?''

``My dear child, it's no use asking me. I'm determined to leave everything to you children this year. Forget I am your mother. Treat me as an honoured guest.''

But Meg could not possibly go and supervise the men. She had washed her hair before breakfast, and she sat drinking her coffee in a green turban\footnote{\textbf{turban} n. a long piece of fabric wound tightly around the head or a woman's hat that looks like it}, with a dark wet curl stamped on each cheek\footnote{\textbf{cheek} n. either side of the face below the eyes}. Jose, the butterfly, always came down in a silk petticoat\footnote{\textbf{petticoat} n. a piece of women's underwear like a thin dress or skirt, worn under a dress or skirt} and a kimono\footnote{\textbf{kimono} n. a traditional Japanese piece of clothing like a long loose dress with wide sleeves, worn on formal occasions} jacket.

``You'll have to go, Laura; you're the artistic one.''

Away Laura flew, still holding her piece of bread-and-butter. It's so delicious to have an excuse for eating out of doors and besides, she loved to arrange things; she always felt she could do it so much better than anybody else.

Four men in their shirt-sleeves\footnote{\textbf{sleeve} n. a part of a piece of colthing that covers all or part of your arm} stood grouped together on the garden path. They carried staves\footnote{\textbf{stave} n. a set of five lines on which music is written} covered with rolls of canvas\footnote{\textbf{canvas} n. a strong heavy rough farbic used for making tents, sails, etc. and by artists for painting on}, and they had big tool-bags slung on their backs. They looked impressive. Laura wished now that she had not got the bread-and-butter, but there was nowhere to put it, and she couldn't possibly throw it away. She blushed\footnote{\textbf{blush} v. to became red in the face because you are embarrassed or ashamed} and tried to look severe\footnote{\textbf{severe} adj. not kind or sympathetic and showing disapproval of sb/sth} and even a little bit short-sighted as she came up to them.

``Good morning,'' she said, copying her mother's voice. But that sounded so fearfully affected that she was ashamed, and stammered\footnote{\textbf{stammer} v. to speak with difficulty, repeating sounds or words and often stopping, before saying things correctly} like a little girl, ``Oh--er--have you come--is it about the marquee?''

``That's right, miss,'' said the tallest of the men, a lanky\footnote{\textbf{lanky} adj. having long thin limbs and moving in an awkward way} freckled\footnote{\textbf{freckled} adj. with a small , pale brown spot on a person's skin, especially on their face, cuased by the sun} fellow, and he shifted his tool-bag, knocked back his straw\footnote{\textbf{straw} n. stems of wheat or other grain plants that have been cut and dried} hat and smiled down at her.

``That's about it.''

His smile was so easy, so friendly that Laura recovered. What nice eyes he had, small, but such a dark blue! And now she looked at the others, they were smiling too. ``Cheer up, we won't bite,'' their smile seemed to say. How very nice workmen were! And what a beautiful morning! She mustn't mention the morning; she must be business-like. The marquee.

``Well, what about the lily-lawn? Would that do?''

And she pointed to the lily-lawn with the hand that didn't hold the bread-and-butter. They turned, they stared in the direction. A little fat chap\footnote{\textbf{chap} n. used to talk about a man in a friendly way} thrust\footnote{\textbf{thrust} v. to push sth/sb suddenly or violently in a particular direction; to move quickly and suddenly in a particular direction} out his under-lip, and the tall fellow frowned\footnote{\textbf{frown} v. to make a serious, angry or worried expression by bring your eyebrows closer together so that lines appear on your forehead}.

``I don't fancy\footnote{\textbf{fancy} v. to want sth or want to do sth} it,'' said he. ``Not conspicuous\footnote{\textbf{conspicuous} adj. easy to see or notice} enough. You see, with a thing like a marquee,'' and he turned to Laura in his easy way, ``you want to put it somewhere where it'll give you a bang slap in the eye, if you follow me.''

Laura's upbringing\footnote{\textbf{upbringing} n. the way in which a child is cared for and taught how to behave while it is growing up} made her wonder for a moment whether it was quite respectful of a workman to talk to her of bangs slap in the eye. But she did quite follow him.

``A corner of the tennis-court,'' she suggested. ``But the band's going to be in one corner.''

``H'm, going to have a band, are you?'' said another of the workmen. He was pale\footnote{\textbf{pale} adj. having skin that is almost white; having skin that is whiter than usual becuase of illness, a strong emotion, etc.}. He had a haggard\footnote{\textbf{haggard} adj. looking very tired because of illness, worry or lack of sleep} look as his dark eyes scanned the tennis-court. What was he thinking?

``Only a very small band,'' said Laura gently. Perhaps he wouldn't mind so much if the band was quite small. But the tall fellow interrupted.

``Look here, miss, that's the place. Against those trees. Over there. That'll do fine.''

Against the karakas\footnote{\textbf{karaka} n. karaka (Corynocarpus laevigatus) is an evergreen tree of the family Corynocarpaceae endemic to New Zealand}. Then the karaka-trees would be hidden. And they were so lovely, with their broad, gleaming\footnote{\textbf{gleam} v. to shine with a pale clear light} leaves, and their clusters of yellow fruit. They were like trees you imagined growing on a desert island, proud, solitary\footnote{\textbf{solitary} adj. alone, with no other people or things around}, lifting their leaves and fruits to the sun in a kind of silent splendour\footnote{\textbf{splendour} n. grand and impressive beauty}. Must they be hidden by a marquee?

They must. Already the men had shouldered their staves and were making for the place, pinched\footnote{\textbf{pinch} v. to hold sth tightly between the thumb and finger of between two things that are pressed together} a sprig\footnote{\textbf{sprig} n. a small stem with leaves on it from a plant or bush, used in cooking or as a decoration} of lavender, put his thumb and forefinger to his nose and snuffed\footnote{\textbf{snuff} v. to smell sth by breathing in noisy through the nose} up the smell. When Laura saw that gesture she forgot all about the karakas in her wonder at him caring for things like that--caring for the smell of lavender. How many men that she knew would have done such a thing? Oh, how extraordinarily nice workmen were, she thought. Why coundn't she have workmen for friends rather than the silly boys she danced with and who came to Sunday night supper? She would get on much better with men like these.

It's all the fault, she decided, as the tall fellow drew something on the back of an envelope, something that was to be looped up or left to hang, of these absurd\footnote{\textbf{absurd} adj. completely ridiculous; not logical and sensible} class distinctions\footnote{\textbf{distinction} n. a clear difference or contrast especially between people or things that are similar or related}. Well, for her part, she didn't feel them. Not a bit, not an atom... And now there came the chock-chock of wooden hammers. Some one whistled, some one sang out, ``Are you right there, matey\footnote{\textbf{matey} n. used by men as an informal way of addressing another man}?'' ``Matey!'' The friendliness of it, the--the-- Just to prove how happy she was, just to show tha tall fellow how at home she felt, and how she despised\footnote{\textbf{despise} v. to dislike and have on respect for sb/sth} stupid conventions\footnote{\textbf{convention} n. the way in which sth is done that most people in a society expect and consider to be polite or the right way to do it; a large meeting of the members of a profession, a political party, etc.}, Laura took a big bite of her bread-and-butter as she stared at the little drawing. She felt just like a work-girl.

``Laura, Laura, where are you? Telephone, Laura!'' a voice cried from the house.

``Coming!'' Away she skimmed\footnote{\textbf{skim} v. to move quickly and lightly over a surface, not touching it or only touching it occasionally}, over the lawn, up the path, up the steps, across the veranda\footnote{\textbf{veranda} n. a platform with an open front and a roof, built onto the side of a house on the ground floor}, and into the porch\footnote{\textbf{porch} n. a small area at the entrance to a building, such as a house or a church, that is covered by a roof and often has walls}. In the hall her father and Laurie were brushing their hats ready to go to the office.

``I say, Laura,'' said Laurie very fast, ``you might just give a squiz\footnote{\textbf{squiz} (AUS/NZL) n. a look or glance} at my coat before this afternoon. See if it wants pressing.''

``I will,'' said she. Suddenly she couldn't stop herself. She ran at Laurie and gave him a small, quick squeeze. ``Oh, I do love parties, don't you?'' gasped\footnote{\textbf{gasp} v. to take a quick deep breath with your mouth open, especially because you are surprised or in pain} Laura.

``Rather,'' said Laurie's warm, boyish voice, and he squeezed his sister too, and gave her a gentle push. ``Dash\footnote{\textbf{dash} v. to go somewhere very quickly} off to the telephone, old girl.''

The telephone. ``Yes, yes; oh yes. Kitty? Good morning, dear. Come to lunch? Do, dear. Delighted\footnote{\textbf{delighted} adj. very pleased} of course. It will only be a very scratch\footnote{\textbf{scratch} adj. put together in a hurry using whatever people or materials are available} meal--just the sandwich crusts\footnote{\textbf{crust} n. the harder outer surface of bread} and broken meringue\footnote{\textbf{meringue} n. a sweet white mixture made from egg whites and sugar, usually baked until crisp and used to make cakes}-shells and what's left over. Yes, isn't it a perfect morning? Your white? Oh, I certainly should. One moment--hold the line. Mother's calling.'' And Laura sat back. ``What, mother? Can't hear.''

Mrs. Sheridan's voice floated down the stairs. ``Tell her to wear that sweet hat she had on last Sunday.''

``Mother says you're to wear that \textit{sweet} hat you had on last Sunday. Good. One o'clock. Bye-bye.''

Laura put back the receiver, flung\footnote{\textbf{fling} v. (pt./pp. \textbf{flung}) to throw sb/sth somewhere with force, especially because you are angry} her arms over her head, took a deep breath, stretched and let them fall. ``Huh,'' she sighed, and the moment after the sigh she sat up quickly. She was still, listening. All the doors in the house seemed to be open. The house was alive with soft, quick steps and running voices. The green baize\footnote{\textbf{baize} n. a thick wollern fabric that is usually green, used especially for covering card tables and billiard, snooker or pool tables} door that led to the kitchen regions swung open and shut with a muffled\footnote{\textbf{muffled} adj. not hear clearly because sth is in the way that stops the sound from travelling easily} thud\footnote{\textbf{thud} n. a sound like the one which is made when a heavy object hits sth else}. And now there came a long, chuckling\footnote{\textbf{chuckle} v. to laugh quietly} absurd sound. It was the heavy piano being moved on its stiff castors. But the air! If you stopped to notice, was the air always like this? Little faint winds were playing chase\footnote{\textbf{chase} n. an act of running or driving after sb/sth in order to catch them; hunting animals as a sport}, in at the tops of the windows, out at the doors. And there were two tiny spots of sun, one on the inkpot, one on a silver photograph frame, playing too. Darling little spots. Especially the one on the inkpot lid. It was quite warm. A warm silver star. She could have kissed it.

The front door bell pealed\footnote{\textbf{peal} v. to ring loudly}, and there sounded the rustle\footnote{\textbf{rustle} n. a light dry sound like paper, leaves, etc. moving or rubbing together} of Sadie's print skirt on the stairs. A man's voice murmured\footnote{\textbf{murmur} v. to say sth in a soft quiet voice that is difficult to hear or understand}; Sadie answered, careless, ``I'm sure I don't know. Wait. I'll ask Mrs. Sheridan.''

``What is it, Sadie?'' Laura came into the hall.

``It's the florist, Miss Laura.''

It was, indeed. There, just inside the door, stood a wide, shallow\footnote{\textbf{shallow} adj. not having much distance between the top or surface and the bottom} tray full of pots of pink lilies. No other kind. Nothing but lilies--canna\footnote{\textbf{canna} n. canna (or canna lily, although not a true lily) is a genus of 19 species of flowering plants} lilies, big pink flowers, wide open, radiant\footnote{\textbf{radiant} adj. showing great happiness, love or health; giving a warm bright light}, almost frighteningly\footnote{\textbf{frightening} adj. making you feel afraid} alive on bright crimson\footnote{\textbf{crimson} adj. dark red in color} stems.

``O-oh, Sadie!'' said Laura, and the sound was like a little moan\footnote{\textbf{moan} n. a long, low sound that someone makes because of pain, unhappiness, or physical pleasure}. She crouched\footnote{\textbf{crouch} v. to lower your body to the ground by bending your legs} down as if to warm herself at that blaze\footnote{\textbf{blaze} n. an intense and dangerous fire} of lilies; she felt they were in her fingers, on her lips, growing in her breast.

``It's some mistake,'' she said faintly. ``Nobody ever ordered so many. Sadie, go and find mother.''

But at that moment Mrs. Sheridan joined them.

``It's quite right,'' she said calmly. ``Yes, I ordered them. Aren't they lovely?'' She pressed Laura's arm. ``I was passing the shop yesterday, and I saw them in the window. And I suddenly thought for once in my life I shall have enough canna lilies. The garden-party will be a good excuse.''

``But I thought you said you didn't mean to interfere\footnote{\textbf{interfere} v. to become involved in the activities and concerns of other people when your involvement is not wanted},'' said Laura. Sadie has gone. The florist's man was still outside at his van\footnote{\textbf{van} n. a vehicle that is used for transporting goods and that is closed in on all sides}. She put her arm round her mother's neck and gently, very gently, she bit her mother's ear.

``My darling child, you wouldn't like a logical mother, would you? Don't do that. Here's the man.''

He carried more lilies still, another whole tray.

``Bank them up, just inside the door, on both sides of the porch, please,'' said Mrs. Sheridan. ``Don't you agree, Laura?''

``Oh, I \textit{do}, mother.''

In the drawing-room Meg, Jose and good little Hans had at last succeeded in moving the piano.

``Now, if we put this chesterfield\footnote{\textbf{chesterfield} n. a couch, sofa, or loveseat with padded arms and back of the same height, often curved outward at the top} against the wall and move everything out of the room except the chairs, don't you think?''

``Ouite.''

``Hans, move these tables into the smoking-room, and bring a sweeper to take these marks off the carpet\footnote{\textbf{carpet} n. a heavy fabric cover for a floor} and--one moment, Hans--'' Jose loved giving orders to the servants, and they loved obeying her. She always made them feel they were taking part in some drama. ``Tell mother and Miss Laura to come here at once.''

``Very good, Miss Jose.''

She turned to Meg. ``I want to hear what the piano sounds like, just in case I'm asked to sing this afternoon. Let's try over `This Life is Weary'.''

\textit{Pom! Ta-ta-ta Tee-ta!} The piano burst out so passionately\footnote{\textbf{passionate} adj. having, showing, or expressing strong emotions or beliefs} that Jose's face changed. She clasped\footnote{\textbf{clasp} v. to hold sb/sth tightly with your hands or arms} her hands. She looked mournfully\footnote{\textbf{mournful} adj. full of sorrow} and enigmatically\footnote{\textbf{enigmatical} adj. full of mystery and difficult to understand} at her mother and Laura as they came in.

\begin{verse}
\textit{This Life is Wee-ary,\\}
\textit{A Tear--a Sigh.\\}
\textit{A Love that Chan-ges,\\}
\textit{This Life is Wee-ary,\\}
\textit{A Tear--a Sigh.\\}
\textit{A Love that Chan-ges,\\}
\textit{And then...Goodbye!}
\end{verse}

But at the word ``Good-bye'', and although the piano sounded more desperate\footnote{\textbf{desperate} adj. feeling or showing despair} than ever, her face broke into a brilliant\footnote{\textbf{brilliant} adj. very bright; very impressive or successful}, dreadfully\footnote{\textbf{dreadful} adj. very bad or unpleasant} unsympathetic\footnote{\textbf{unsympathetic} adj. not sympathetic; not feeling or showing concern about someone who is in a bad situation} smile.

``Aren't I in good voice, mummy?'' she beamed.

\begin{verse}
\textit{This Life is Wee-ary,\\}
\textit{Hope comes to Die.\\}
\textit{A Dream--a Wa-kening.}
\end{verse}

But now Sadie interrupted them. ``What is it, Sadie?''

``If you please, m'm, cook says have you got the flags for the sandwiches?''

``The flags for the sandwiches, Sadie?'' echoed Mrs. Sheridan dreamily. And the children knew by her face that she hadn't got them. ``Let me see.'' And she said to Sadie firmly, ``Tell cook I'll let her have them in ten minutes.''

Sadie went.

``Now, Laura,'' said her mother quickly. ``Come with me into the smoking-room. I've got the names somewhere on the back of an envelope. You'll have to write them out for me. Meg, go upstairs this minute and take that wet thing off your head. Jose, run and finish dressing this instant. Do you hear me, children, or shall I have to tell your father when he comes home tonight? And--and, Jose, pacify\footnote{\textbf{pacify} v. to cause (someone who is angry or upset) to become calm or quiet} cook if you do go into the kitchen, will you? I'm terrified of her this morning.''

The envelope was found at last behind the dining-room clock, though how it had got there Mrs. Sheridan could not imagine.

``One of you children must have stolen it out of my bag, because I rememver vividly--cream cheese and lemon-curd. Have you done that?''

``Yes.''

``Egg and--'' Mrs. Sheridan held the envelope away from her. ``It looks like mice. It can't be mice, can it?''

``Olive\footnote{\textbf{olive} n. a small, egg-shaped black or green fruit that is used as food or for making oil}, pet,'' said Laura, looking over her shoulder.

``Yes, of course, olive. What a horrible combination it sounds. Egg and olive.''

They were finished at last, and Laura took them off to the kitchen. She found Jose there pacifying the cook, who did not look at all terrifying\footnote{\textbf{terrify} v. to cause (sb) to be extremely afraid}.

``I have never seen such exquisite\footnote{\textbf{exquisite} adj. finely done or made} sandwiches,'' said Jose's rapturous\footnote{\textbf{rapturous} adj. showing extreme pleasure, love, or enthusiasm for someone or sth} voice. ``How many kinds did you say there were, cook? Fifteen?''

``Fifteen, Miss Jose.''

``Well, cook, I congratulate you.''

Cook swept up crusts with the long sandwich knife, and smiled broadly.

``Godber's has come,'' announced Sadie, issuing out of the pantry\footnote{\textbf{pantry} n. a small room in a house in which food is stored}. She had seen the man pass the window.

That meant the cream puffs\footnote{\textbf{puff} n. a light, round pastry that contains a sweet filling} had come. Godber's were famous for their cream puffs. Nobody ever thought of making them at home.

``Bring them in and put them on the table, my girl,'' ordered cook.

Sadie brought them in and went back to the door. Of course Laura and Jose were far too grown-up to really care about such things. All the same, they couldn't help agreeing that the puffs looked very attractive. Very. Cook began arranging them, shaking off the extra icing sugar.

``Don't the carry one back to all one's parties?'' said Laura.

``I suppose they do,'' said practical Jose, who never liked to be carried back. ``They look beautifully light and feathery\footnote{\textbf{feathery} adj. extremely light and soft or delicate}, I must say.''

``Have one each, my dears,'' said cook in her comfortable voice. ``Yer ma won't know.''

Oh, impossible. Fancy cream puffs so soon after breakfast. The very idea made one shudder\footnote{\textbf{shudder} v. to shake because of fear, cold, etc.}. All the same, two minutes later Jose and Laura were licking\footnote{\textbf{lick} v. to pass the tongue over} their fingers with that absorbed\footnote{\textbf{absorb} v. to take up the whole interest or attention of (someone)} inward look that only comes from whipped\footnote{\textbf{whip} v. to move quickly or forcefully} cream.

``Let's go into the garden, out by the back way,'' suggested Laura. ``I want to see how the men are getting on with the marquee. They're such awfully nice men.''

But the back door was blocked by cook, Sadie, Godber's man and Hans.

Something had happened.

``Tuk-tuk-tuk,'' clucked\footnote{\textbf{cluck} v. to make a low sound with the tongue} cook like an agitated\footnote{\textbf{agitate} v. to disturb, excite, or anger (someone)} hen, Sadie had her hand clapped to her cheek as though she had toothache. Hans's face was screwed up in the effort to understand. Only Godber's man seemed to be enjoying himself; it was his story.

``What's the matter? What's happened?''

``There's been a horrible accident,'' said cook. ``A man killed.''

``A man killed! Where? How? When?''

But Godber's man wasn't going to have his story snatched\footnote{\textbf{snatch} v. to take (sth) quickly or eagerly} from under his very nose.

``Know those little cottages just below here, miss?'' Know them? Of course, she knew them. ``Well, there's a young chap living there, name of Scott, a carter\footnote{\textbf{carter} n. a person who hauls goods in a cart}. His horse shied at a traction\footnote{\textbf{traction} n. the force that causes a moving thing to stick against the surface it is moving along}-engine, corner of Hawke Street this morning, and he was thrown out on the back of his head. Killed.''

``Dead!'' Laura stared at Godber's man.

``Dead when they picked him up,'' said Godber's man with relish\footnote{\textbf{relish} n. enjoyment of or delight in sth}. ``They were taking the body home as I come up here.'' And he said to the cook, ``He's left a wife and five little ones.''

``Jose, come here.'' Laura caught hold of her sister's sleeve and dragged her through the kitchen to the other side of the green baize door. There she paused and leaned\footnote{\textbf{lean} v. to bend or move from a straight position} against it. ``Jose!'' she said, horrified\footnote{\textbf{horrify} v. to cause (someone) to feel horror or shock}, ``however are we going to stop everything?''

``Stop everything, Laura!'' cried Jose in astonishment\footnote{\textbf{astonishment} n. a feeling of being very surprised}. ``What do you mean?''

``Stop the garden-party, of course.'' Why did Jose pretend?

But Jose was still more amazed. ``Stop the garden-party? My dear Laura, don't be so absurd. Of course we can't do anything of the kind. Nobody expects us to. Don't be so extravagant\footnote{\textbf{extravagant} adj. more than is usual, necessary, or proper}.''

``But we can't possibly have a garden-party with a man dead just outside thr front gate.''

That really was extravagant, for the little cottages were in a lane\footnote{\textbf{lane} n. a narrow road or path} to themselves at the very bottom of a steep\footnote{\textbf{steep} adj. almost straight up and down} rise that led up to the house. A broad road ran between. True, they were far too near. They were the greatest possible eyesore\footnote{\textbf{eyesore} n. an ugly object or building}, and they had no right to be in the neighbourhood at all. They were little mean dwellings\footnote{\textbf{dwelling} n. a place where a person lives} painted a chocolate brown. In the garden patches there was nothing but cabbage stalks\footnote{\textbf{stalk} n. a thick or tall stem of a plant}, sick hens and tomato cans. The very smoke coming out of their chimneys\footnote{\textbf{chimney} n. a part of building through which smoke rises into the outisde air} was poverty-stricken. Little rags\footnote{\textbf{rag} n. a piece of cloth that is old and no longer in good condition} and shreds\footnote{\textbf{shred} n. a long, thin piece cut or torn off of sth} of smoke, so unlike the great silvery\footnote{\textbf{silvery} adj. shiny and white or light gray in color like silver} plumes\footnote{\textbf{plume} n. a feather or group of feathers on a bird} that uncurled\footnote{\textbf{uncurl} v. to make (sth that is curled or coiled) straight} from the Sheridans' chimneys. Washer-women lived in the lane and sweeps and a cobbler\footnote{\textbf{cobbler} n. a person who makes or repairs shoes}, and a man whose house-front was studded\footnote{\textbf{stud} v. to decorate or cover (sth) with many small items} all over with minute bird-cages. Children swarmed. When the Sheridans were little they were forbidden to set foot there because of the revolting\footnote{\textbf{revolting} adj. extremely unpleasant of offensive} language and of what they might catch. But since they were grown up, Laura and Laurie on the prowls\footnote{\textbf{prowl} n. an act of moving through a place while searching for sth} sometimes walked through. It was disgusting\footnote{\textbf{disgusting} adj. so unpleasant to see, smell, taste, consider, etc., that you feel slightly sick} and sordid\footnote{\textbf{sordid} adj. very bad or dishonest}. They came out with a shudder. But still one must go everywhere; one must see everything. So through they went.

``And just think of what the band would sound like to that poor woman,'' said Laura.

``Oh, Laura!'' Jose began to be seriously annoyed\footnote{\textbf{annoy} v. to cause (someone) to feel slightly angry}. ``If you're going to stop a band playing every time some one has an accident, you'll lead a very strenuous\footnote{\textbf{strenuous} adj. requiring or showing great energy and efforrequiring or showing great energy and effortt} life. I'm every bit as sorry about it as you. I feel just as sympathetic\footnote{\textbf{sympathetic} adj. feeling or showing concern about someone who is in a bad situation}.'' Her eyes hardened. She looked at her sister just as she used to when they were little and fighting together. ``You won't bring a drunken workman back to life by being sentimental\footnote{\textbf{sentimental} adj. based on, showing, or resulting from feelings or emotions rather than reason or thought},'' she said softly.

``Drunk! Who said he was drunk?'' Laura turned furiously\footnote{\textbf{furious} adj. very angry} on Jose. She said, just as they had used to say on those occasions, ``I'm going straight up to tell mother.''

``Do, dear,'' cooed\footnote{\textbf{coo} v. to talk in a soft, quiet, and loving way} Jose.

``Mother, can I come into your room?'' Laura turned the big glass doorknob\footnote{\textbf{doorknob} n. a round handle that you turn to open a door}.

``Of course, child. Why, what's the matter? What's given you such a colour?'' And Mrs. Sheridan turned round from her dressing-table. She was trying on a new hat.

``Mother, a man's been killed,'' began Laura.

``Not in the garden?'' interrupted her mother.

``No, no!''

``Oh, what a fright\footnote{\textbf{fright} n. fear caused by sudden danger} you gave me!'' Mrs. Sheridan sighed with relief\footnote{\textbf{relief} n. feeling that someone has when sth unpleasant stops or does not happen}, and took off the big hat and held it on her knees.

``But listen, mother,'' said Laura. Breathless\footnote{\textbf{breathless} adj. unable to take enough air into your lungs}, half-choking\footnote{\textbf{choke} v. to become unable to breathe usually because sth gets stuck in your throat or because the air is not good for breathing}, she told the dreadful story. ``Of course, we can't have our party, can we?'' she pleaded\footnote{\textbf{plead} v. to ask for sth in a serious and emotional way}. ``The band and everybody arriving. They'd hear us, mother; they'er nearly neighbours!''

To Laura's astonishment her mother behaved just like Jose; it was harder to hear because she seemed amused\footnote{\textbf{amuse} v. to make someone laugh or smile}. She refused to take Laura seriously.

``But, my dear child, use your common sense. It's only by accident we've heard of it. If some one had died there normally--and I can't understand how they keep alive in those poky\footnote{\textbf{poky} adj. small and uncomfortable} little holes--we should still be having our party, shouldn't we?''

Laura had to say ``yes'' to that, but she felt it was all wrong. She sat down on her mother's sofa and pinched the cushion\footnote{\textbf{cushion} n. a soft object or part that is used to make sth (such as a seat) more comfortable or to protect a surface from damage} frill\footnote{\textbf{frill} n. a strip of cloth that is gathered into folds on one edge and attached to sth (such as clothing or curtains) as a decoration}.

``Mother, isn't it really terribly heartless of us?'' she asked.

``Darling!'' Mrs. Sheridan got up and came over to her, carring the hat. Before Laura could stop her she had popped it on\footnote{\textbf{pop (sth) on} pr.v. to put on (clothing) quickly}. ``My child!'' said her mother, ``the hat is yours. It's made for you. It's much too young for me. I have never seen you look such a picture. Look at yourself!'' And she held up her hand-mirror.

``But, mother,'' Laura began again. She couldn't look at herself; she turned aside.

This time Mrs. Sheridan lost patience just as Jose had done.

``You're being very absurd, Laura,'' she said coldly. ``People like that don't expect sacrifices\footnote{\textbf{sacrifice} n. the act of giving up sth that you want to keep especially in order to get or do sth else or to help someone} from us. And it's not very sympathetic to spoil everybody's enjoyment as you're doing now.''

``I don't understand,'' said Laura, and she walked quickly out of the room into her own bedroom. There, quite by chance, the first thing she saw was this charming\footnote{\textbf{charming} adj. very pleasing or appealing} girl in the mirror, in her black hat trimmed\footnote{\textbf{trim} v. to decorate (sth) especially around the edges with ribbons, ornaments, etc.} with gold daisies, and a long black velvet\footnote{\textbf{velvet} n. a soft type of cloth that has short raised fibers on one side} ribbon. Never had she imagined she could look like that. Is mother right? she thought. And now she hoped her mother was right. Am I being extravagant? Perhaps it was extravagant. Just for a moment she had another glimpse\footnote{\textbf{glimpse} n. a brief or quick view or look} of that poor women and those little children, and the body being carried into the house. But it all seemed blurred, unreal, like a picture in the newspaper. I'll remember it again after the party's over, she decided. And somehow that seemed quite the best plan...

Lunch was over by half-past one. By half-past two they were all ready for the fray\footnote{\textbf{fray} n. a fight, struggle, or disagreement that involves many people}. The green-coated band had arrived and was established\footnote{\textbf{establish} v. to put (someone or sth) in a position, role, etc., that will last for a long time} in a corner of the tennis-court.

``My dear!'' trilled\footnote{\textbf{trill} v. to make a series of quick high sounds} Kitty Maitland, ``aren't they too like frogs for words? You ought to have arranged them round the pond with the conductor in the middle on a leaf.''

Laurie arrived and hailed\footnote{\textbf{hail} v. to speak of or welcome (someone or sth) with praise or enthusiasm} them on his way to dress. At the sight of him Laura remembered the accident again. She wanted to tell him. If Laurie agreed with the others, then it was bound to be all right. And she followed him into the hall.

``Laurie!''

``Hallo\footnote{\textbf{hallo} n. aka. hello}!'' He was half-way upstairs, but when he turned round and saw Laura he suddenly puffed out his cheeks and goggled\footnote{\textbf{goggle} v. to look at sth or someone with your eyes very open in a way that shows that shows that you are surprised, amazed, etc.} his eyes at her. ``My word, Laura! You do look stunning\footnote{\textbf{stunning} adj. very surprising or shocking},'' said Laurie. ``What an absolutely topping hat!''

Laura said faintly ``Is it?'' and smiled up at Laurie, and didn't tell him after all.

Soon after that people began coming in streams. The band struck up; the hired waiters ran from the house to the marquee. Wherever you looked there were couples strolling\footnote{\textbf{stroll} v. to walk slowly in usually a pleasant and relaxed way}, bending\footnote{\textbf{bend} v. to move your body so that it is not straight} to the flowers, greeting, moving on over the lawn. They were like bright birds that had alighted\footnote{\textbf{alight} v. to stop on a surface after flying} in the Sheridans' garden for this one afternoon, on their way to where? Ah, what happiness it is to be with people who all are happy, to press hands, press cheeks, smile into eyes.

``Darling Laura, how well you look!''

``What a becoming hat, child!''

``Laura, you look quite Spanish. I've never seen you look so striking\footnote{\textbf{striking} adj. unusual or extreme in a way that attracts attention}.''

And Laura, glowing\footnote{\textbf{glowing} adj. very enthusiastic}, answered softly. ``Have you had tea? Won't you have an ice? The passion-fruit\footnote{\textbf{passion-fruit} n. passiflora edulis is a vine species of passion flower that is native to Brazil, Paraguay and northern Argentina, its common names include passion fruit (US), passionfruit (UK and Commonwealth), and purple granadilla (South Africa)} ices really are rather special.'' She ran to her father and begged him. ``Daddy darling, can't the band have something to drink?''

And the perfect afternoon slowly ripened\footnote{\textbf{ripen} v. to make (sth) ripe}, slowly faded\footnote{\textbf{fade} v. to disappear gradually}, slowly its petals\footnote{\textbf{petal} n. one of the soft, colorful parts of a flower} closed.

``Never a more delightful\footnote{\textbf{delightful} adj. very pleasant} garden party...'' ``The greatest success...'' ``Quite the most...''

Laura helped her mother with goodbyes. They stood side by side in the porch till it was all over.

``All over, all over, thank heaven,'' said Mrs. Sheridan. ``Round up the others, Laura. Let's go and have some fresh coffee. I'm exhausted\footnote{\textbf{exhaust} v. to use all of someone's mental or physical energy}. Yes, it's been very successful. But oh, these parties, these parties! Why will you children insist on giving parties!'' And they all of them sat down in the deserted marquee.

``Have a sandwich, daddy dear. I wrote the flag.''

``Thanks.'' Mr. Sheridan took a bite and the sandwich was gone. He took another. ``I suppose you didn't hear of a beastly\footnote{\textbf{beastly} adj. very unpleasant} accident that happened today?'' he said.

``My dear,'' said Mrs. Sheridan, holding up her hand, ``we did. It nearly ruined the party. Laura insisted we should put it off.''

``Oh, mother!'' Laura didn't want to be teased\footnote{\textbf{tease} v. to laugh at and criticize (someone) in a way that is either friendly and playful or cruel and unkind} about it.

``It was a horrible affair all the same,'' said Mr. Sheridan. ``The chap was married too. Lived just below in the lane, and leaves a wife and half a dozen kiddies\footnote{\textbf{kiddie} n. a young child}, so they say.''

An awkward\footnote{\textbf{awkward} adj. not graceful} little silence fell. Mrs. Sheridan fidgeted\footnote{\textbf{fidget} v. to make a lot of small movements because you are nervous, bored, etc.} with her cup. Really, it was very tactless\footnote{\textbf{tactless} adj. tending to offend or upset people} of father ...

Suddenly she looked up. There on the table were all those sandwiches, cakes, puffs, all uneaten, all going to be wasted. She had one of her brilliant ideas.

``I know,'' she said. ``Let's make up a basket. Let's send that poor creature some of this perfectly good food. At any rate, it will be the greatest treat for the children. Don't you agree? And she's sure to have neighbours calling in and so on. What a point to have it all ready prepared. Laura!'' She jumped up. ``Get me the big basket out of the stairs cupboard.''

``But, mother, do you really think it's a good idea?'' said Laura.

Again, how curious\footnote{\textbf{curious} adj. having a desire to learn or know more about sth or someone}, she seemed to be different from them all. To take scraps\footnote{\textbf{scrap} n. a very small amount-- usually used in negative statements} from their party. Would the poor woman really like that?

``Of course! What's the matter with you today? An hour or two ago you were insisting on us being sympathetic, and now--''

Oh, well! Laura ran for the basket. It was filled, it was heaped\footnote{\textbf{heap} v. to put (sth) in a large pile} by her mother.

``Take it yourself, darling,'' said she. ``Run down just as you are. No, wait, take the arum lilies\footnote{\textbf{arum lily} n. Zantedeschia,  is a genus of eight species of herbaceous perennial flowering plants in the family Araceae, native to southern Africa from South Africa north to Malawi} too. People of that class are so impressed by arum lilies.''

``The stems will ruin her lace\footnote{\textbf{lace} n. a very thin and light cloth made with patterns of holes} frock\footnote{\textbf{frock} n. (old-fashioned) a woman's or girl's dress},'' said practical Jose.

So they would. Just in time. ``Only the basket, then. And, Laura!''-- her mother followed her out of the marquee-- ``don't on any account--''

``What, mother?''

No, better not put such ideas into the child's head! ``Nothing! Run along.''
