\lettrine{M}{y} beautiful new watch had run eighteen months without losing or gaining, and without breaking any part of its machinery\footnote{\textbf{machinery} n. the working parts of a machine} or stopping. I had come to believe it infallible\footnote{\textbf{infallible} adj. not capable of being wrong or making mistakes} in its judgments about time of day, and to consider its constitution and its anatomy\footnote{\textbf{anatomy} n. the parts or causes that form or create sth} imperishable\footnote{\textbf{imperishable} adj. never to be forgotten}. But at last, one night, I let it run down. I grieved\footnote{\textbf{grieve} v. to cause (someone) to feel sad or unhappy} about it as if it were a recognized messenger and forerunner\footnote{\textbf{forerunner} n. a sign of sth that is going to happen} of calamity\footnote{\textbf{calamity} n. an event that causes great harm and suffering}. But by and by I cheered up, set the watch by guess, and commanded my bodings\footnote{\textbf{bode} v. (\textbf{n.} boding) to be a sign of (a future event or situation)} and superstitions\footnote{\textbf{superstition} n. a belief or way of behaving that is based on fear of the unknown and faith in magic or luck} to depart. Next day I stepped into the chief jeweler's to set it by the exact time, and the head of the establishment\footnote{\textbf{establishment} n. a place or organization where people live or do business} took it out of my hand and preceeded to set it for me. Then he said, ``She is four minutes slow--regulator\footnote{\textbf{regulator} n. a device for controlling the level or amount of sth (such as speed or temperature)} wants pushing up.'' I tried to stop him--tried to make him understand that the watch kept perfect time. But no; all this human cabbage\footnote{\textbf{cabbage} n. a person who leads a dull or inactive life} could see was that the watch was four minutes slow, and the regulator \textit{must} be pushed up a little; and so, while I danced around him in anguish\footnote{\textbf{anguish} n. extreme suffering, grief, or pain}, and implored\footnote{\textbf{implore} v. to make a very serious or emotional request to (someone)} him to let the watch alone, he calmly and cruelly\footnote{\textbf{cruel} adj. (\textbf{adv.} cruelly) used to describe people who hurt others and do not feel sorry about it} did the shameful deed. My watch began to gain. It gained faster and faster day by day. Within the week it sickened\footnote{\textbf{sicken} v. to become sick or to cause (someone) to become sick} to a raging\footnote{\textbf{raging} adj. causing a lot of pain or distress} fever, and its pulse\footnote{\textbf{pulse} n. a strong, regular beat or pattern of sounds in music} went up to a hundred and fifty in the shade. At the end of two months it had left all the timepieces of the town far in the rear, and was a fraction\footnote{\textbf{fraction} n. a part of amount of sth} over thirteen days ahead of the almanac\footnote{\textbf{almanac} n. a book published every year that contains facts about the movements of the sun and moon, changes in the tides, and information of general interest}. It was away into November enjoying the snow, while the October leaves were still turning. It hurried up house rent, bills payable, and such things, in such a ruinous\footnote{\textbf{ruinous} adj. causing or likely to cause damage or destruction} way that I could not abide\footnote{\textbf{abide} v. to accpet or bear (someone or sth bad, unpleasant, etc.)} it. I took it to the watchmaker to be regulated\footnote{\textbf{regulate} v. to set or adjust the amount, degree, or rate of (sth)}. He asked me if I had ever had it repaired. I said no, it had never needed any repairing. He looked a look of vicious\footnote{\textbf{vicious} adj. very violent and cruel} happiness and eagerly pried\footnote{\textbf{pry} v. to raise, move, or open (sth) with a tool} the watch open, and then put a small dice-box into his eye and peered\footnote{\textbf{peer} v. to look closely or carefully especially because sth or someone is difficult to see} into its machinery. He said it wanted cleaning and oiling, besides regulating--come in a week. After being cleaned and oiled, and regulated, my watch slowed down to that degree that it ticked like a tolling\footnote{\textbf{toll} v. to ring slowly} bell. I began to be left by trains, I failed all appointments, I got to missing my dinner; my watch strung\footnote{\textbf{string} v. (pt./pp. \textbf{strung}) (string out) to make (sth) take longer that it should} out three days' grace to four and let me go to protest\footnote{\textbf{protest} n. sth said or done that shows disagreement with or disapproval of sth}; I gradually drifted\footnote{\textbf{drift} v. to change slowly from one state or condition to another} back into yesterday, then day before, then into last week, and by and by the comperhension came upon me that all solitary and alone I was lingering along in week before last, and the world was out of sight. I seemed to detect in myself a sort of sneaking fellow-feeling for the mummy in the museum, and a desire to swap news with him. I went to a watchmaker again. He took the watch all to pieces while I waited, and then said the barrel was ``swelled\footnote{\textbf{swell} v. to become larger than normal}''. He said he could reduce it in three days. After this the watch \textit{averaged} well, but nothing more. For half a day it would go like the very mischief\footnote{\textbf{mischief} n. behavior or activity that is annoying but that is not meant to cause serious harm or damage}, and keep up such a barking and wheezing and whooping and sneezing and snorting, that I could not hear myself think for the disturbance; and as long as it held out there was not a watch in the land that stood any chance against it. But the rest of the day it would keep on slowing down and fooling along until all the clocks it had left behind caught up again. So at last, at the end of twenty-four hours, it would trot\footnote{\textbf{trot} v. to move quickly} up to the judges' stand all right and just in time. It would show a fair and square average, and no man could say it had done more or less than its duty. But a correct average is only a mild\footnote{\textbf{mild} adj. gentle in nature or behavior} virtue\footnote{\textbf{virtue} n. a good and moral quality} in a watch, and I took this instrument to another watchmaker. He said the king-bolt\footnote{\textbf{king-bolt} n. a vertical bolt by which the forward axle and wheels of a vehicle or the trucks of a railroad car are connected with the other parts} was broken. I said I was glad it was nothing more serious. To tell the plain truth, I had no idea what the king-bolt was, but I did not choose to appear ignorant\footnote{\textbf{ignorant} adj. lacking knowledge or information} to a stranger. He repaired the king-bolt, but what the watch gained in one way it lost in another. It would run awhile and then stop awhile, and then run awhile again, and so on, using its own discretion\footnote{\textbf{discretion} n. the right to choose what should be done in a particular situation} about the intervals. And every time it went off it kicked back like a musket\footnote{\textbf{musket} n. a type of long gun that was used by soldiers before the invention of the rifle}. I padded my breast for a few days, but finally took the watch to another watchmaker. He picked it all to pieces, and turned the ruin over and over under his glass; and then he said there appeared to be something the matter with the hair-trigger. He fixed it, and gave it a fresh start. It did well now, except that always at ten minutes to ten the hands would shut together like a pair of scissors, and from that time forth they would travel together. The oldest man in the world could not make head or tail of the time of day by such a watch, and so I went again to have the repaired. This person said that the crystal had got bent, and that the mainspring was not straight.
